**Preprinting Microbiology**

### 2017-01-06 submission/Schloss_PrePrints_mBio_2017.Rmd
Rough in analysis section

library(rjson)
biorxiv <- fromJSON(readLines('data/processed/biorxiv_data_summary.json'))

@@

## Preprints in microbiology

***Preprint metrics in microbiology.*** To analyze the use of preprints, we copied the bioRxiv website on December 31, 2016. We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r length(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*. Among the `r length(biorxiv)` preprints on bioRxiv, **XXXX** were assigned by the authors into the Microbiology category. When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified **XXXX** additional manuscripts. These microbiology-affiliated preprints were primarily assigned to the **XXXX (N=XX)**, **XXXX (N=XX)**, or **XXXX (N=XX)** categories. One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint. For example, this manuscript could be assigned to either the Microbiology or Scientific Communication and Education categories.

Questions:
* How many preprints are being submitted each month - microbiology category and microbiology-ish
* What fraction of PPs are now published that were deposited before January 1, 2016?
* How many times is each preprint revised (perhaps looking at those that have been published)
* How do PP altmetrics compare to ASM altmetrics over the same time span?
* Where do microbiology/microbiology-affiliated preprints come from?
* How many microbiology/microbiology-affiliated preprints do people submit?

* Distribution of downloads
* Distribution of abstract hits

* Would love to calculate a JIF of preprints with and without those that have not yet been published.

***Microbiology anecdotes.***
* MinIon methods
* PacBio paper
* Tardigrade microbiome
* NYC subway microbiome

***Specific challenges for microbiology.***
* Dual use
* Protection of human subjects
* Conflicts of interest

@@

>>>>

@@

```{r analysis}
library(dplyr)

biorxiv <- read.table(file = 'data/processed/biorxiv_data_summary.tsv')

```
## Preprints in microbiology

***Metrics for microbiology preprints.*** To analyze the use of preprints, we copied the bioRxiv website on December 31, 2016. We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r length(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*. Among the `r length(biorxiv)` preprints on bioRxiv, **XXXX** were assigned by the authors into the Microbiology category. When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified **XXXX** additional manuscripts (**Figure 1**). These microbiology-affiliated preprints were primarily assigned to the **XXXX (N=XX)**, **XXXX (N=XX)**, or **XXXX (N=XX)** categories. One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint. For example, this manuscript could be assigned to either the Microbiology or Scientific Communication and Education categories. Reflecting the still relatively novelty of preprints, **XX** (**XX**%) corresponding authors who submitted a microbiology-affiliated manuscript (N=**XXX** total) have posted a single preprint and **XX**% have submitted more than 3. Corresponding authors that have posted microbiology-affiliated preprints are primarily affiliated with institutions in the United States (**XX**%), **XXXXX XXXXXX** (**XX**%),  and **XXXXX XXXXXX** (**XX**%).

As stated above, preprints offer researchers the opportunity to improve the quality of their work by adding a more formal and public step to the scientific process. Among the microbiology-affiliated manuscripts, only **XX** (**XX**%) had been commented on at least once and only **XX** (**XX**%) more than three times using the *bioRxiv*-hosted commenting feature. Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback. Regardless, authors do appear to be incorporating feedback from colleagues or editorial insights from journals as they post a median of **XX** versions of each preprints (IQR: **XX-XX**). Among the preprints posted prior to January 1, 2016, **XXX**% of the Microbiology category preprints, **XX**% of the microbiology-affiliated preprints, and **XX**% of all preprints have been published. Considering that these "acceptance rates" are relatively high compared to most peer-reviewed journals (e.g. 25% at ASM Journals), these results would appear to dispel the critique that preprints represent overly preliminary research.

Measuring the impact and significance of scientific research is notoriously difficult. Using several metrics, we sought to quantify the effect that preprints have had on the scholarly work of others. Using the download statistics associated with each preprint, we found that the median number of times an abstract or PDF had been accessed was **XXX** (IQR: **XX-XX**) and **XXX** (IQR: **XX-XX**), respectively. These values represent two aspects of posting a preprint. First, they reflect the number of times people were able to access science before it was published. Second, they reflect the number of times people were able to access a version of a manuscript that is published behind a paywall. To obtain a measure of a preprint's ability to garner attention and engage the public, we obtained the Altmetric Attention Score for each preprint. This score measures the number of times a preprint or paper is mentioned in social media, mainstream media, peer reviews, and policy documents. Microbiology-affiliated preprints have had a median Altmetric Attention Score of **XXX** (IQR: **XX-XX**) and those of all preprints hosted at *bioRxiv* have had a median score of **XXX** (IQR: **XX-XX**). For comparison, the median Altmetric Attention Score for ASM journal articles for articles posted since November 2013 was **XXX** (IQR: **XX-XX**). A more traditional and controversial metric of impact has been the number of citations an article receives. We obtained the number of citations for the published versions of manuscripts that were initially posted as preprints. To allow for a comparison to traditional journals, we considered the citations for preprints posted in 2014 and 2015 as aggregated by Web of Science. Among the preprints that were published, the median number of citations was **XXX** (IQR: **XX-XX**; mean: **XX.X**) and if unpublished preprints were included the median number of citations was **XXX** (IQR: **XX-XX**; mean: **XX.X**). These values are comparable to many popular microbiology journals. *Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community*

***Microbiology anecdotes.***
* MinIon methods
* Tardigrade microbiome
* NYC subway microbiome

***Specific challenges for microbiology.*** Although preprints offer an efficient and novel venue for disseminating microbiology research, there are several considerations that the scientific community and those that oversee preprint servers must consider. It is critical that assurances be given that policies are in place to address these issues. First, a significant amount of attention has been given to the potential dual use of microbiology research for individuals seeking to engage in terrorist activities. Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research. Third, there is significant concern regarding researchers hiding potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results. Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism. Microbiology journals have policies in place to address these issues that should be easily implemented by preprint servers.

@@

## Figures

**Figure 1. **
* How many preprints are being submitted each month - microbiology category and microbiology-ish
